---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# youtubecaption

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/jooyoungseo/youtubecaption.svg?branch=master)](https://travis-ci.org/jooyoungseo/youtubecaption)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/jooyoungseo/youtubecaption?branch=master&svg=true)](https://ci.appveyor.com/project/jooyoungseo/youtubecaption)
[![Codecov test coverage](https://codecov.io/gh/jooyoungseo/youtubecaption/branch/master/graph/badge.svg)](https://codecov.io/gh/jooyoungseo/youtubecaption?branch=master)
<!-- badges: end -->

## Motivation

Although there exist some R packages tailored for YouTube API (e.g., 'tuber'), downloading YouTube video subtitle (i.e., caption) in a tidy form has never been a low-hanging fruit. Using 'youtube-transcript-api' Python package under the hood, this R package provides users with a convenient way of parsing and converting a desired YouTube caption into a handy tibble data_frame object. Furthermore, users can easily save a desired YouTube caption data as a tidy Excel file without advanced programming background knowledge.

## Installation

### Python Dependencies

`youtubecaption` requires Anaconda Python environment on your system Path.

If you have not installed Conda environment on your system, please [download and install Anaconda](https://www.anaconda.com/download/) (Python 3.6 or later is recommended).

For this package, I have employed [**youtube-transcript-api**](https://pypi.org/project/youtube-transcript-api/) Python module into R using [**reticulate**](https://rstudio.github.io/reticulate/).

### R Package Installation

#### Development Version

You can install the latest development version as follows:

```{r, eval=FALSE}
if(!require(remotes)) {
install.packages("remotes")
}

remotes::install_github("jooyoungseo/youtubecaption")
```

### Stable Version

You can install the released version of youtubecaption from [CRAN](https://CRAN.R-project.org) with:

```{r, eval=FALSE}
install.packages('youtubecaption')
```

## Usage

Please use `get_caption()` function after loading `youtubecaption` package like below:

```{r test, tidy=TRUE, eval=FALSE}
library(youtubecaption)

# Let's get the video caption out of Hadley Wickham's "You can't do data science in a GUI":
url <- "https://www.youtube.com/watch?v=cpbtcsGE0OA"
caption <- get_caption(url)
caption

#> # A tibble: 1,420 x 5
#>    segment_id text                                start duration vid       
#>         <int> <chr>                               <dbl>    <dbl> <chr>     
#>  1          1 thank you for coming to a meeting ~  7.13     8.32 cpbtcsGE0~
#>  2          2 in regards to data science GUI with 10.7      8.44 cpbtcsGE0~
#>  3          3 happy with chief data scientist in~ 15.4      7.11 cpbtcsGE0~
#>  4          4 studio as well as the member of th~ 19.1      7.23 cpbtcsGE0~
#>  5          5 Foundation and an attempt professo~ 22.6      6    cpbtcsGE0~
#>  6          6 Stanford and at the University of   26.4      6.48 cpbtcsGE0~
#>  7          7 Auckland he builds both computatio~ 28.6      7.17 cpbtcsGE0~
#>  8          8 and cognitive tools to make data s~ 32.8      7.5  cpbtcsGE0~
#>  9          9 easier faster and more times his w~ 35.7      7.01 cpbtcsGE0~
#> 10         10 includes various packages as well ~ 40.4      6.21 cpbtcsGE0~
#> # ... with 1,410 more rows

# Save the caption as an Excel file and open it right it away:
get_caption(url = url, savexl = TRUE, openxl = TRUE)
```
